working title Compatibility system and stygma size of pollen recipient as main predictors of heterospecific pollen effect

### 2018-12-12 Manuscript_draft/Manuscript_draft.Rmd
some changes

>>>>

Ideas about pollen size in heterospecific pollen effect. (still have to develop it more...)

Let's classify pollen size in three groups in order to understand the interaction between pollen donor and recipient. 
Donor's pollen:
1) Donor pollen size < Recipient pollen size
2) Donor pollen size = Recipient pollen size
3) Donor pollen size > Recipient pollen size

Small pollen can clogg the stigma. YES. Big pollen doesn't fit in very small stigmas. YES.

Is small pollen likely to affect bigger pollen. Ideas: It can be compensated with, less number of ovules to fertilize and faster pollen tube growth. So generally speaking, when the differences in pollen size are evident we expect a similar outcome.

### 2018-12-12 Manuscript_draft/Manuscript_draft.tex
some changes

>>>>

Ideas about pollen size in heterospecific pollen effect. (still have to
develop it more\ldots{})

Let's classify pollen size in three groups in order to understand the
interaction between pollen donor and recipient. Donor's pollen: 1) Donor
pollen size \textless{} Recipient pollen size 2) Donor pollen size =
Recipient pollen size 3) Donor pollen size \textgreater{} Recipient
pollen size

Small pollen can clogg the stigma. YES. Big pollen doesn't fit in very
small stigmas. YES.

Is small pollen likely to affect bigger pollen. Ideas: It can be
compensated with, less number of ovules to fertilize and faster pollen
tube growth. So generally speaking, when the differences in pollen size
are evident we expect a similar outcome.
